Reasoning About a Machine with Local Capabilities

### 2019-08-19 toplas/paper.tex
[TOPLAS] Add sentence to Sewel discussion

\begin{toplas}
  \emph{Why use a logical relation and not a simpler proof technique?}
  The concept of a capability exists on different levels of abstraction on computers, so capabilities have been studied and safety properties proven about them in other contexts than assembly languages.
  Traditionally, logical relations have not been used for safety property proofs, so why do we need one here?
  To answer this question let's compare this work to \citet{sewel_integrity_2011} where they prove \textit{integrity} and \textit{authority confinement} for the seL4 Microkernel.
  % Describe what they prove
  The security properties they show are relative to a security policy that specifies the upperbound of capabilities a subject in the system can posses.
  The security policy is expressed as a collection of possible capabilities in the system, e.g.\ \textit{subject A can have a write capability for memory B.}
  However, their policy are, in a sense, binary: subject a can either not write or write anything to memory B.
  Our approach is much more fine-grained and allows us to define, for example, a policy that subject a can write to memory B, but only if the value is an even number.
  Because our invariants are indexed by worlds themselves, we can even define a policy that capabilities written to memory B must respect certain other invariants themselves.
  It is exactly the expressive invariants that enable us to prove the awkward example.
  We place a protocol on the memory where variable \texttt{x} is stored that says that it sometimes can be either $0$ or $1$ and at other times it has to be $1$.

>>>>

\begin{toplas}
  \emph{Why use a logical relation and not a simpler proof technique?}
  The concept of a capability exists on different levels of abstraction on computers, so capabilities have been studied and safety properties proven about them in other contexts than assembly languages.
  Traditionally, logical relations have not been used for safety property proofs, so why do we need one here?
  To answer this question let's compare this work to \citet{sewel_integrity_2011} where they prove \textit{integrity} and \textit{authority confinement} for the seL4 Microkernel.
  % Describe what they prove
  The security properties they show are relative to a security policy that specifies the upperbound of capabilities a subject in the system can posses.
  The security policy is expressed as a collection of possible capabilities in the system, e.g.\ \textit{subject A can have a write capability for memory B.}
  However, their policy are, in a sense, binary: subject A is either allowed to write to memory B or not.
  If writing is allowed, then any value can be written, as long as that value is itself legal.
  \citet{sewel_integrity_2011}'s results are not parametrised by a (possibly more restrictive) policy that subject A should observe on memory B.
  Our approach is much more fine-grained and allows us to define, for example, a policy that subject A can write to memory B, but only if the value is an even number.
  Because our invariants are indexed by worlds themselves, we can even define a policy that capabilities written to memory B must respect certain other invariants themselves.
  It is exactly the expressive invariants that enable us to prove the awkward example.
  We place a protocol on the memory where variable \texttt{x} is stored that says that it sometimes can be either $0$ or $1$ and at other times it has to be $1$.
